%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[colorlinks,linkcolor=blue,citecolor=blue]{hyperref}
\usepackage[left=1in,top=1.5in,right=1in,bottom=1in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}


\name{Jiashuo Jiang} % Your name% Your phone number and email
\address{(+1)~347-463-0062 \\ jj2398@stern.nyu.edu}
\address{44 W 4th St, New York City, NY, 10014}
\address{\url{https://jiashuo3.github.io/}}

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------


\begin{rSection}{Education}

{\bf Ph.D. in Operations Management, New York University} \hfill {\em Sept. 2017 - Jan. 2023}
\\ \ Department of Technologies, Operations and Statistics
\\ \ Stern School of Business
\\ \ advised by Prof. Jiawei Zhang and Prof. Will Ma


{\bf B.S. in Mathematics, Peking University} \hfill {\em Sept. 2013 - June. 2017}
\\School of Mathematical Sciences


\end{rSection}
\vspace{0.2cm}


\begin{rSection}{Research Interests}
Applications: supply chain management; inventory system; revenue management. \\
Methodologies: online optimization and learning; stochastic optimization; applied probability.
\end{rSection}

\vspace{0.2cm}

\begin{rSection}{Teaching Experience}
\vspace{-0.3cm}
\item[] \textbf{Operations Management (undergraduate core)}, NYU Stern (2021)\\
\small
  \ Role: instructor\\
  \ Course evaluation: 4.7/5\\
  \ Enrollment: 16

\end{rSection}
\smallskip

\begin{rSection}{Other Experiences}
\vspace{-0.3cm}
\item[1.] Summer internship at \textit{Amazon Supply Chain Optimization Technologies (SCOT) department}\\
\small
  \ Role: research scientist\\
  \ Project: applying data-driven online optimization techniques to enhance the inbound process management for Amazon supply chain system.

\item[2.] Visiting graduate student at \textit{Simons Institue for the Theory of Computing}\\
\small
  \ Role: participating in the \textit{data-driven decision processes} program.

\end{rSection}
\smallskip


\begin{rSection}{Publications}

\begin{enumerate}

\item[1.] \textbf{Achieving High Individual Service-Levels without Safety Stock? Optimal Rationing Policy of Pooled Resources.}\label{P3} \\
\small
 \ Authors: Jiashuo Jiang, Shixin Wang, Jiawei Zhang \\
 \ Outlet: \textit{Operations Research 2022 (article in advance)}
\normalsize

\item[2.] \textbf{Tight Guarantees for Multi-unit Prophet Inequalities and Online Stochastic Knapsack.}\label{P1} \\
\small
 \ Authors: Jiashuo Jiang, Will Ma, Jiawei Zhang \\
 \ An extended abstract accepted by \textit{SODA 2022} \\
 \ Journal version under review at \textit{Operations Research}\\
 \ Finalist for 2021 Jeff McGill Student Paper Award for Revenue Management and Pricing\\
 \ Finalist for 2022 George Nicholson Student Paper Competition
\normalsize

\item[3.] \textbf{Non-stationary Bandits with Knapsacks.}\label{P5} \\
\small
 \ Authors: Shang Liu, Jiashuo Jiang, Jiawei Zhang \\
 \ Outlet: \textit{NeurIPS 2022}
\normalsize

\end{enumerate}

\end{rSection}
\vspace{0.3cm}

\begin{rSection}{Preprints and Papers Under Review}

\begin{enumerate}

\item[4.] \textbf{Online Stochastic Optimization with Wasserstein Based Non-stationarity.}\label{P2} \\
\small
 \ Authors: Jiashuo Jiang, Xiaocheng Li, Jiawei Zhang \\
 \ Outlet: Under Review after a major revision at \textit{Management Science}
\normalsize

\item[5.] \textbf{Learning to Order for Inventory Systems with Lost Sales and Uncertain Supplies.}\label{P7} \\
\small
 \ Authors: Boxiao Chen, Jiashuo Jiang, Jiawei Zhang, Zhengyuan Zhou \\
 \ Outlet: Under Review at \textit{Management Science}
\normalsize

\item[6.] \textbf{Tightness without Counterexamples: A New Approach and New Results for Prophet Inequalities.}\label{P6} \\
\small
 \ Authors: Jiashuo Jiang, Will Ma, Jiawei Zhang \\
 \ Outlet: In Preparation for Submission to \textit{Operations Research}
\normalsize

\item[7.] \textbf{Degeneracy is OK: Logarithmic Regret for Network Revenue Management with Indiscrete Distributions.}\label{P8} \\
\small
 \ Authors: Jiashuo Jiang, Will Ma, Jiawei Zhang \\
 \ Outlet: In Preparation for Submission to \textit{Operations Research}
\normalsize

\item[8.] \textbf{Online Resource Allocation with Stochastic Resource Consumption.}\label{P4} \\
\small
 \ Authors: Jiashuo Jiang, Jiawei Zhang \\
 \ Outlet: Working paper
\normalsize

\end{enumerate}

\end{rSection}
\vspace{0.3cm}



\begin{rSection}{Academic Services}
\vspace{-0.3cm}
\item[1.] Session chair for Informs 2022.

\item[2.] Session chair for the 2022 CORS/INFORMS International Conference.

\item[3.] Review for \textit{Operations Research, Management Science, Mathematics of Operations Research, Informs Journal on Computing}.

\item[4.] Organizer for the NYU Stern MOILS seminar (2019).

\end{rSection}
\smallskip



%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\vspace{0.3cm}

\begin{rSection}{Invited Conference/Seminar Presentations}
\vspace{-0.3cm}
\item[1.] \textbf{``Achieving High Individual Service-Levels without Safety Stock? Optimal Rationing Policy of Pooled Resources''} \\
 \ \ Informs Annual Meeting at Seattle, WA  \hfill{Oct. 2019}\\
\vspace{0.1cm}

\item[2.] \textbf{``Online Resource Allocation with Stochastic Resource Consumption''} \\
 \ \ Informs Annual Meeting at Seattle, WA \hfill{Oct. 2019} \\
 \ \ NYU Stern MOILS seminar at NYC, NY \hfill{May. 2019}\\
 \vspace{0.1cm}

\item[3.] \textbf{``Tight Guarantees for Multi-unit Prophet Inequalities and Online Stochastic Knapsack''}\\
 \ \ NYU Stern MOILS seminar at NYC, NY \hfill{May. 2021}\\
 \ \ INFORMS Revenue Management and Pricing (RMP) Section Conference (virtual) \hfill{June. 2021}\\
 \ \ Cornell ORIE young researcher workshop at Ithaca, NY \hfill{Oct. 2021}\\
 \ \ Informs Annual Meeting at Anaheim, CA \hfill{Oct. 2021}\\
 \ \ Informs Optimization Society Conference at Greenville, SC \hfill{Mar. 2022}\\
 \ \ Microsoft Marketplace Innovation Workshop (virtual) \hfill{May. 2022}\\
 \ \ Informs Annual Meeting at Indianapolis, IN \hfill{Oct. 2022}\\
\vspace{0.1cm}

\item[4.] \textbf{``Online Stochastic Optimization with Wasserstein Based Non-stationarity''}\\
 \ \ NYU Stern MOILS seminar at NYC, NY \hfill{Nov. 2020}\\
 \ \ INFORMS Revenue Management and Pricing (RMP) Section Conference (virtual) \hfill{June. 2021}\\
 \ \ Manufacturing and Service Operations Management Society Conference (virtual) \hfill{June. 2021}\\
 \ \ Informs Annual Meeting at Anaheim, CA \hfill{Oct. 2021}\\
 \ \ Informs Optimization Society Conference at Greenville, SC \hfill{Mar. 2022}\\
\vspace{0.1cm}

\item[5.] \textbf{``Degeneracy is OK: Logarithmic Regret for Network Revenue Management with Indiscrete Distributions''}\\
 \ \ Informs Annual Meeting at Indianapolis, IN \hfill{Oct. 2022}\\
\end{rSection}
\smallskip

\vspace{0.3cm}

%\begin{rSection}{other professional activities}
%Reviewer for \textit{Mathematics of Operations Research}, \textit{Operations Research}, \textit{Management Science} and \textit{Informs Journal on Computing}\\
%Coordinator for NYU Stern MOILS seminar (2019)

%\end{rSection}
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%\newpage
%\begin{rSection}{References}
% 	\vspace{0.3cm}
%	
% 	\begin{tabular}{lr}
%		\small
% 		% Referee 1
%		 \begin{minipage}[t]{3in}
% 			{\bf Jiawei Zhang}\\
% 			Professor\\
%             NYU Stern\\
% 			\url{jz31@stern.nyu.edu}
% 		\end{minipage}
%
%		 \begin{minipage}[t]{3in}
% 			{\bf Will Ma}\\
% 			Assistant Professor\\
%           Columbia University\\
% 			\url{wm2428@gsb.columbia.edu}
% 		\end{minipage}\vspace{0.3cm}
%		
% 		\\ % Additional newline for spacing.
% 		% Referee 3
%		
%		\small
%\begin{minipage}[t]{3in}
% 			{\bf Xiaocheng Li}\\
% 			Assistant Professor\\
%            Imperial College Business School\\
% 			\url{xiaocheng.li@imperial.ac.uk}
% 		\end{minipage}
%
%         \begin{minipage}[t]{3in}
% 			{\bf Ilan Lobel}\\
% 			Associate Professor\\
%            NYU Stern\\
% 			\url{ilobel@stern.nyu.edu}
% 		\end{minipage}\vspace{0.3cm}
% %\\
%
% %\begin{minipage}[t]{2.1in}
%% 			{\bf Zhengyuan Zhou}\\
%% 			Assistant Professor\\
%%            NYU Stern\\
%% 			\url{zzhou@stern.nyu.edu}
%% 		\end{minipage}
%		
% 	\end{tabular}
% 	
%
% 	\normalsize
%\end{rSection}
%
%	\normalsize
%\vspace{0.3cm}

%\begin{rSection}{Other Experiences} \itemsep -2pt
%\item Association of Chinese Students and Scholars at Stanford (ACSSS), Co-President (2016-2017) \\
%Association of Chinese Students and Scholars at Stanford (ACSSS), Vice President (2015-2016)
%
%\item Graduate Student Council of Stanford University, Voting Member/Representative at Large (2016-2017)
%
%\item Student Chapter of INFORMS at Stanford University, CFO (2017-2018)
%
%\item Consulting Experiences:
%
%\begin{itemize}
%\item Swiss Re (Sept. 2018 - Apr. 2019) \\
%Developed a machine learning/deep learning model for corporate credit risk modeling.
%
%\item Haulistix (Aug. 2019 - Present)\\
%A start-up company on data-driven logistics management
%
%\item Afresh Technologies Inc. (July 2018)\\
%A start-up company on perishable product inventory management
%
%\item Data Scientist Internship at Apple (Summer 2016) \\
%Designed and implemented two machine learning based modules for optimizing hardware production and anomaly detection on web logs.
%\end{itemize}
%\end{rSection}
%\smallskip



\end{document}
